\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{listings}

\title{Decentralized Pokémon Trading Platform}
\author{mserra}
\date{March 2025}

\begin{document}

\maketitle
\tableofcontents
\newpage

\section{Overview}
This project is a decentralized application (dApp) that allows users to mint, own, and trade Pokémon cards as NFTs using the Ethereum blockchain. The dApp is built with Solidity (smart contracts), Hardhat (development environment), React (frontend), and Ethers.js (blockchain interaction).

\section{Project Architecture}
\subsection{Components}
\begin{itemize}
    \item \textbf{Smart Contracts (Solidity, Hardhat)}
    \begin{itemize}
        \item \texttt{PokemonNFT.sol}: Implements the ERC721 standard for Pokémon NFTs.
        \item Functions:
        \begin{itemize}
            \item \texttt{mintPokemon(address player, string name, string pokeType, uint256 level)}
            \item \texttt{getPokemonDetails(uint256 tokenId)}
            \item \texttt{ownerOf(uint256 tokenId)}
        \end{itemize}
    \end{itemize}
    \item \textbf{Backend (Hardhat Local Testnet)}
    \begin{itemize}
        \item Local Ethereum blockchain for development \& testing.
    \end{itemize}
    \item \textbf{Frontend (React, Ethers.js, MetaMask Integration)}
    \begin{itemize}
        \item Connects to MetaMask for user authentication.
        \item Allows users to mint Pokémon NFTs.
        \item Displays owned Pokémon.
    \end{itemize}
\end{itemize}

\section{Issues and Challenges}
During the development and operation of the platform, we have encountered the following issues:
\begin{enumerate}
    \item \textbf{Transaction Failures and Delays}: Some transactions fail or experience significant delays due to network congestion and smart contract limitations.
    \item \textbf{Inaccurate Pokémon Data}: There are occasional discrepancies where Pokémon attributes (such as level or type) are not updated correctly.
    \item \textbf{High Transaction Fees}: Users may experience high gas fees during peak trading periods, increasing the cost of transactions.
    \item \textbf{User Interface Glitches}: Inconsistent behavior in the UI can cause confusion during trade execution.
    \item \textbf{Smart Contract Vulnerabilities}: Security audits have revealed potential vulnerabilities that are currently being addressed.
    \item \textbf{Decentralized Order Matching Issues}: The matching engine sometimes fails to efficiently pair trade offers, resulting in unmatched orders.
    \item \textbf{Wallet Integration Problems}: Some users have experienced difficulties connecting external wallets, affecting smooth trade execution.
\end{enumerate}

\section{Setup Instructions}
\subsection{Prerequisites}
Ensure you have the following installed:
\begin{itemize}
    \item Node.js (v18 or v20 recommended)
    \item MetaMask browser extension
    \item Hardhat (Ethereum development framework)
    \item VS Code or another code editor
\end{itemize}

\subsection{Clone the Repository}
\begin{lstlisting}
git clone https://github.com/your-repo/pokemon-nft-dapp.git
cd pokemon-nft-dapp
\end{lstlisting}

\subsection{Install Dependencies}
\textbf{Backend Dependencies:}
\begin{lstlisting}
cd defi-pokemon
npm install
\end{lstlisting}
\textbf{Frontend Dependencies:}
\begin{lstlisting}
cd frontend
npm install
\end{lstlisting}

\subsection{Compile and Deploy Smart Contracts}
\textbf{Start Hardhat Local Network:}
\begin{lstlisting}
npx hardhat node
\end{lstlisting}
\textbf{Deploy the Contract:}
\begin{lstlisting}
npx hardhat run scripts/deploy.js --network localhost
\end{lstlisting}
\textbf{Copy the deployed contract address from the output.}

\subsection{Configure Frontend}
Open \texttt{frontend/src/App.js} and replace this line with your contract address:
\begin{lstlisting}
const contractAddress = "0xYourContractAddress";
\end{lstlisting}

\subsection{Run the Frontend}
\begin{lstlisting}
cd frontend
npm start
\end{lstlisting}
Open your browser and go to \texttt{http://localhost:3000/}.

\section{User Guide}
\subsection{Connect MetaMask}
\begin{itemize}
    \item Click \textbf{"Connect MetaMask"}.
    \item Approve wallet connection.
    \item Your Ethereum address will be displayed.
\end{itemize}

\subsection{Mint a Pokémon NFT}
\begin{itemize}
    \item Enter \textbf{Pokémon Name, Type, Level}.
    \item Click \textbf{"Mint Pokémon"}.
    \item Approve the transaction in MetaMask.
    \item The minted Pokémon appears under \textbf{"My Pokémon"}.
\end{itemize}

\subsection{View Owned Pokémon}
\begin{itemize}
    \item The UI lists all Pokémon owned by the connected wallet.
\end{itemize}

\subsection{Troubleshooting Known Issues}
If you encounter problems, consider the following steps:
\begin{itemize}
    \item \textbf{Transaction Delays/Failures}: Wait a few minutes and try again. Ensure you have set an adequate gas fee.
    \item \textbf{Inaccurate Pokémon Data}: Refresh the page or re-fetch data to verify updated information.
    \item \textbf{High Gas Fees}: Try executing transactions during off-peak hours.
    \item \textbf{UI Glitches}: Clear your browser cache or restart the application.
    \item \textbf{Wallet Connection Issues}: Disconnect and reconnect MetaMask, or try using a different browser.
\end{itemize}

\section{Future Enhancements}
\begin{itemize}
    \item \textbf{NFT Marketplace}: Enable trading of Pokémon NFTs.
    \item \textbf{Pokémon Transfers}: Allow users to transfer NFTs to others.
    \item \textbf{UI Enhancements}: Display Pokémon images and improve overall design.
    \item \textbf{Deploy to Public Testnet}: Deploy on Ethereum public testnets such as Goerli or Sepolia.
\end{itemize}

\section{Technical Support \& References}
\begin{itemize}
    \item \href{https://hardhat.org/}{Hardhat Documentation}
    \item \href{https://docs.openzeppelin.com/contracts/}{OpenZeppelin Contracts}
    \item \href{https://docs.ethers.io/}{Ethers.js}
    \item \href{https://metamask.io/}{MetaMask}
\end{itemize}

\end{document}
